Test susieI using whole genome, s40.22 samples

### 2020-11-04 analysis/simulation-susieI-ukbWG-gtex.adipose_s40.22.Rmd
SER

@@

```{r param1susie, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config1.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config1.susieI.txt")

df <- show_param(phenofs, susieIfs, susieIfs2)
par(mfrow = c(2,2))
plot_param(df[1:5,], main = "low power")
plot_param(df[6:10,], main = "high power")
```

@@

```{r param1, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config1.SERIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config1.SERI.txt")

df <- show_param(phenofs, susieIfs, susieIfs2)
par(mfrow = c(2,2))
plot_param(df[1:5,], main = "low power")
plot_param(df[6:10,], main = "high power")
```

@@

```{r param6, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config6.SERIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config6.SERI.txt")

df <- show_param(phenofs, susieIfs, susieIfs2)
par(mfrow = c(2,2))
plot_param(df[1:5,], main = "low power")
plot_param(df[6:10,], main = "high power")
```

@@

```{r param7, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config7.SERIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config7.SERI.txt")

df <- show_param(phenofs, susieIfs, susieIfs2)
par(mfrow = c(2,2))
plot_param(df[1:5,], main = "low power")
plot_param(df[6:10,], main = "high power")
```

>>>>

  st <-  cbind(df[,"pi1.SNP_susietruth"], 1:nrow(df), 2 + 1:nrow(df)/nrow(df)/3)
  s <- cbind(df[,"pi1.SNP_susieI"], 1:nrow(df), 3 + 1:nrow(df)/nrow(df)/3)
  t <- df[1,"pi1.SNP_truth"]
  dfp <- rbind(st,s)
  plot(dfp[,3], dfp[,1], col = dfp[,2], pch = 19, ylab = "SNP pi1", xaxt = "n", xlab="", xlim = c(0.8, 3.5), frame.plot=FALSE, ylim = c(0, max(dfp[,1],t) *1.05), ...)
  axis(side=1, at=1:2, labels = FALSE, tick = F)
  text(x=2:3, 0, labels = c( "susieI_truth", "susieI"), xpd = T, pos =1)
  abline(h=t, lty = 2, col= "salmon", lwd=1.5)
  grid()

@@

```{r param1susie, fig.height=6, fig.width=8}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config1.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config1.susieI.txt")

df <- show_param(phenofs, susieIfs, susieIfs2)
par(mfrow = c(2,3))
plot_param(df[1:5,], main = "low power")
plot_param(df[6:10,], main = "high power")
```

@@

```{r param1, fig.height=6, fig.width=8}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config1.SERIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config1.SERI.txt")

df <- show_param(phenofs, susieIfs, susieIfs2)
par(mfrow = c(2,3))
plot_param(df[1:5,], main = "low power")
plot_param(df[6:10,], main = "high power")
```

@@

```{r param6, fig.height=6, fig.width=8}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config6.SERIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config6.SERI.txt")

df <- show_param(phenofs, susieIfs, susieIfs2)
par(mfrow = c(2,3))
plot_param(df[1:5,], main = "low power")
plot_param(df[6:10,], main = "high power")
```

@@

```{r param7, fig.height=6, fig.width=8}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config7.SERIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config7.SERI.txt")

df <- show_param(phenofs, susieIfs, susieIfs2)
par(mfrow = c(2,3))
plot_param(df[1:5,], main = "low power")
plot_param(df[6:10,], main = "high power")
```
